Supplementary material

### 2020-04-23 analysis/paper/supplementary.Rmd
Paper and supplementary changed - Bibliography solved on paper.rmd - Minor changes to text and spelling - References to figures, tables and supplementary solved
- Minor changes to rmd
- Added table with dates
- Spacing and floats solved

---
title: "Supplementary material"
header-includes:
  - \usepackage{caption}
  - \captionsetup[figure]{name=Supplementary Figure,labelfont=it,labelsep = period}
  - \captionsetup[table]{name=Supplementary Table,labelfont=it,labelsep = period}  
output: 
  pdf_document: 
    latex_engine: xelatex
    fig_caption: no

@@

# Call packages
library(readr)
library(dplyr)
library(stringr)
library(tidyr)
library(knitr)
library(tab)
library(ggplot2)
library(FactoMineR)
library(factoextra)
library(RcmdrMisc)
library(IDPmisc)
library(forcats)
library(kableExtra)
library(float)
library(janitor)
library(ggpubr)
library(ggExtra)
library(ggsci)
library(ggalluvial)
```

@@

@@

>>>>

---
title: "Supplementary material"
header-includes:
  - \usepackage{caption}
  - \captionsetup[figure]{name=Supplementary Figure,labelfont=it,labelsep = period}
  - \captionsetup[table]{name=Supplementary Table,labelfont=it,labelsep = period}  
output: 
  pdf_document: 
    latex_engine: xelatex

@@

# Call packages
library(readr)
library(dplyr)
library(stringr)
library(tidyr)
library(knitr)
library(tab)
library(ggplot2)
library(FactoMineR)
library(factoextra)
library(RcmdrMisc)
library(IDPmisc)
library(forcats)
library(kableExtra)
library(float)
library(janitor)
library(ggpubr)
library(ggExtra)
library(ggsci)
library(ggalluvial)
library(Bchron)
library(plyr)
```

@@

\clearpage

@@

```{r datesproto, include=FALSE}

####
# Adapted from Marwick et al. 2017
dates <- read_csv(here::here("analysis/data/raw_data/Dates (non cal).csv"))
ages <- BchronCalibrate(ages=dates$`Age (BP)`,
                        ageSds=dates$SD,
                        calCurves=dates$Curve)
#summary(ages)
#plot(ages, withPositions=TRUE)
age_samples = lapply(ages, function(x) sample(x$ageGrid,size=2000,replace=TRUE,prob=x$densities))
df <- ldply(age_samples,quantile,prob=c(0.025,0.975))
dates_table <- dates[, c("Site",  "Level", "Lab. Ref",  "Age (BP)", "SD",
                         "Sample type")]
dates_table <- cbind(dates_table, df[,-1])
dates_table$`2.5%` <- round(dates_table$`2.5%`, 0)
dates_table$`97.5%`  <- round(dates_table$`97.5%`, 0)

row.names(dates_table) <- NULL

names(dates_table) <- c("Site",  "Level", "Lab. Ref",  "Age (BP)", "SD",
                        "Sample type", "Calibrated lower 95%", "Calibrated upper 95%")

```{r protodates, echo=FALSE}
knitr::kable(dates_table, booktabs=TRUE, longtable = TRUE, caption = "Summary of radiocarbon dates from Portuguese Proto-Solutrean. Adapted from Zilhão (1997), Cascalheira and Bicho (2013), Belmiro (2018) and Benedetti et al. (2019). Calibration curves are IntCal13 and Marine13, using OxCal 4.1.7 (online).") %>% 
  column_spec(1, bold = T) %>% 
  kable_styling(latex_options = c("repeat_header"), font_size = 9) %>% 
  landscape()
```
